Fisher’s Method

### 2019-01-16 Fishers_method/Fishers_method_101518.Rmd
updated files for rpp and rpe plots and tables with new simulation data

Table: Power of Fisher's method given large sample sizes for varying $\delta$ and true # of non-null effects (i.e. "Best-case scenario")
```{r, echo=FALSE}
library(knitr)
table <- readRDS("./power_large_n.RDS")
kable(table,format="markdown",digits=4,align=c('l','r','r','r'),col.names=c("# of non-null effects","$\\delta=0.2$","$\\delta=0.5$","$\\delta=0.8$"),caption="Power to reject H0 with large n")
```
[^3]:Note that because we are working with a set of replicate studies which found a p-value greater than 0.05, pairing large effects with very large sample sizes is not realistic, and therefore we begin the simulations with the largest $n_j$ among the studies for which the power is at most 99.99% to detect the given $\delta_j$. The largest sample sizes used for $\delta_j=0.2; 0.5$; and $0.8$ were $n_j=745; 159;$ and $100$ respectively. See Appendix A.2 for further discussion.

>>>>

Table: Power of Fisher's method given large sample sizes for varying $\delta$ and true # of non-null effects (i.e. "Best-case scenario")
```{r, echo=FALSE}
library(knitr)
table <- readRDS("./power_large_n.RDS")
kable(table,format="markdown",digits=4,align=c('l','r','r','r'),col.names=c("# of non-null effects","$\\delta=0.2$","$\\delta=0.5$","$\\delta=0.8$"),caption="Power to reject H0 with large n")

table <- spread(all_power_results, key = delta, value = power)
table_rpp <- table[table$study == "RPP", -c(1,3, 4)]
table_rpe <- table[table$study == "RPE", -c(1,3, 4)]
kable(table_rpp, format="markdown", digits=4, align=c('l','r','r','r'),row.names = FALSE, col.names=c("# of false negatives","$\\delta=0.2$","$\\delta=0.5$","$\\delta=0.8$"),caption="RPP: Power to reject H0 with large n")

kable(table_rpe, format="markdown", digits=4, align=c('l','r','r','r'),row.names = FALSE, col.names=c("# of false negatives","$\\delta=0.2$","$\\delta=0.5$","$\\delta=0.8$"),caption="RPE: Power to reject H0 with large n")
```
[^3]:Note that because we are working with a set of replicate studies which found a p-value greater than 0.05, pairing large effects with very large sample sizes is not realistic, and therefore we begin the simulations with the largest $n_j$ among the studies for which the power is at most 99.99% to detect the given $\delta_j$. The largest sample sizes used for $\delta_j=0.2; 0.5$; and $0.8$ were $n_j=745; 159;$ and $100$ respectively. See Appendix A.2 for further discussion.
